
An example R-package demonstrating linking against lvec
=======================================================

[`lvec`](https://github.com/djvanderlaan/lvec) is an package that allows one to
work with vectors that are too large to fit into memory. It does that by storing
the data partially on disk. `lvec` contains some basic functionality for
reading, writing and modifying an `lvec` object from R. With this functionality
many of the operations one might like to do can be implemented directly in R.
However, some operations can be performed much more efficiently directly in C++
(the language in which the core of `lvec` is implmented). Thefore, `lvec`
exports the necessary headers and functions, so that dependent methods can work
with `lvec` objects in C++. 

This repository contains an example package showing how a package can work with
an `lvec` object in C++. 




Comparison of different methods to calculate the sum of an lvec
----------------------------------------------------------------

The package implements four different methods for calculating the sum of an
`lvec`. They are described and benchmarked below.

1. Use the `get_of_type` method, to convert each value in the `lvec` to double
   and sum those.
2. Use the visitor pattern to write a template function that handles each type
   of `lvec`. 
3. Assume the `lvec` is of type double; cast the `lvec` to an lvec of type 
   double and throw an error otherwise. 
4. Process the `lvec` in R using chunks.


```{r}
library(lvec.example)
library(microbenchmark)

x <- as_lvec(rnorm(5E6))

microbenchmark(
  sum1(x),
  sum2(x),
  sum3(x),
  sum4(x), times = 25
)
```

Comparison of different methode to calculate the square of an lvec
------------------------------------------------------------------

The package contains two methods to calculate the square of an lvec. This 
demonstrates how one can generate and return a new `lvec`. 

1. An implementation in c++ using the visitor pattern. 
2. An implementation in R using chunks. 


```{r}
microbenchmark(
  square(x),
  square_r(x), times = 25
)
```
